Transfer report

### 2018-09-24 Report/paper-story.Rmd
Updates the paper with mixed models instead of between subject anovas

```{r setup, include=FALSE}
library(ggplot2)
library(ez)
library(Hmisc)
library(dplyr)
library(reshape2)
library(broom)
library(knitr)
library(papaja)

@@

Specific tests (hypothesis in parenthesis)
- Overrall average walking performance in phase 1 vs phase 2 
- Performance in block 4 vs performance in block 1 and 2

- Overrall average pointing performance in phase 1 vs phase 2 
- Average walking perfomrance in block 3 vs 4 (block directly before vs directly after the switch)
- Personal walking performance change in block 3 vs 4 (calculated as an average of individuals (block3-block4)/(block3+block4))
- Personal walking performance change in block 1 vs 4 (calculated as an average of individuals (block1-block4)/(block3+block4))
- level of correlation of personal performance in block 1,2,3 and 4 - higher transfer should show higher correlation in these comparisons
- Difference in performance between groups in blocks 5 and 6 (e.g. not immediately after the switch, but after all groups have been subjected the real world environment for some time)
- Difference in performance between groups in block 4-6 with inclusion of VR-VR group nad real-VR group (to see if the final performance is subjected to the necessity of a real world experience, or not and to see if the swith has detrimental effect on real-VR as well).

@@

### Performance in block 4 is better than in block 1
If we assume some level of transfer, than the average or individual performance in block 4 should be better in all conditions than in block 1 or potentially in block 2. I don't test for block 3 because that immediately compares the switch performance. 
```{r, echo=F,message=F}
make_graph(sub_walk_all[sub_walk_all$exp_block_id %in% c(1,4),], "learning.condition", "min_norm_distance", "exp_block_id") + 
  ylab("Average normalised trial distance") + xlab("condition") + 
  scale_fill_manual(values=estimote_pal,"Block ID")
make_graph(sub_walk_all[sub_walk_all$exp_block_id %in% c(1,4),], "learning.condition", "errors", "exp_block_id") + 
  ylab("Average number of errors") + xlab("condition") + 
  scale_fill_manual(values=estimote_pal,"Block ID")
```

@@

Anova shows a significant effect of phase and condition on overall performance, but not of their interaction.
```{r, echo=F}
kable(apa_print(aov(min_norm_distance ~ phase*learning.condition, sub_walk_all))$table)
pair_t_norm_distance_phase_2 <- pairwise.t.test(sub_walk_all$min_norm_distance, sub_walk_all$learning.condition, p.adj = "holm")
```
Performance in the second phase differs significantly between groups (`r apa_print(aov(min_norm_distance ~ learning.condition, sub_walk_all[sub_walk_all$phase == 2,]))$statistic$learning_condition`), suggesting that the learnign modality has an effect on the overall performance. Tukey test shows significant difference between real adn a desktop versions. although this can be only because of bad performance in block 4 after switch, not due to blocks 5 and 6 (will test later.)

@@

Anova shows significant effect of both phase, learning condition and their interaction on pointing performance. Probably due to the fact that participants pointed less acurately on the treadmill and evn less on the desktop, but all then achieved same performance by the end of the 6th block.
```{r, echo=F}
kable(apa_print(aov(abs_error ~ phase*learning.condition, sub_sop_all))$table)
```

### Average walking perfomrance in block 3 vs 4

@@

Running pairwise t-tests to see performance change from block 3 to 4 gives the following results.
```{r, echo=F}
df_dist <- block_t_test(sub_walk_all, 3, 4,"min_norm_distance")[,c(1,4)]
df_error <- block_t_test(sub_walk_all, 3, 4,"errors")[,c(1,4)]
df34 <- merge(df_dist, df_error, by = "learning.condition")
colnames(df34) <- c("learning condition", "p-value distance improvement", "p-value errors improvement")
kable(df34, caption="Paired T test comparing infividual performance improvement from block 3-4 in different conditions")
```

@@

ggplot(clean_walk_34, aes(x = as.numeric(exp_block_id), y = errors, color = factor(condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(width=0.1), width = 0.2, geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_identity(), size = 1, geom="line") + 
  ylab("Average number of errors") + xlab("Experimental block") + 
  scale_color_manual(values = estimote_pal, "Learning condition")
```
### Personal walking performance change in block 1 vs 4 
(calculated as an average of individuals (block1-block4)/(block3+block4))
```{r, echo=F}
df_wide_errors$block14 <- (df_wide_errors$block1-df_wide_errors$block4)/(df_wide_errors$block1+df_wide_errors$block4)
df_wide_distance$block14 <- (df_wide_distance$block1-df_wide_distance$block4)/(df_wide_distance$block1+df_wide_distance$block4)
clean_walk_14 <- ez_prepare_block(sub_walk_all, c(1,4))
```

@@

### level of correlation of personal performance in block 1,2,3 and 4

@@

POtential followups
### difference in performance between groups in blocks 5 and 6

@@

```
### difference in performance between groups in block 4-6 with inclusion of VR-VR group nad real-VR group

>>>>

```{r setup, include=FALSE}
library(ggplot2)
library(ez)
library(Hmisc)
library(dplyr)
library(reshape2)
library(broom)
library(knitr)
library(ez)
library(lme4)
library(car)
library(papaja)

@@

Specific tests
- Overrall average walking performance in phase 1 vs phase 2 
- Performance in block 4 vs performance in block 1 and 2

- Overrall average pointing performance in phase 1 vs phase 2 
- Average walking perfomrance in block 3 vs 4 (block directly before vs directly after the switch)
- Personal walking performance change in block 3 vs 4 (calculated as an average of individuals (block3-block4)/(block3+block4))
- Personal walking performance change in block 1 vs 4 (calculated as an average of individuals (block1-block4)/(block3+block4))
- Learning modality has an effect on the learning curve (slope)
- Level of correlation of personal performance in block 1,2,3 and 4 - higher transfer should show higher correlation in these comparisons
- Difference in performance between groups in blocks 5 and 6 (e.g. not immediately after the switch, but after all groups have been subjected the real world environment for some time)
- Difference in performance between groups in block 4-6 with inclusion of VR-VR group nad real-VR group (to see if the final performance is subjected to the necessity of a real world experience, or not and to see if the swith has detrimental effect on real-VR as well).

@@

### Performance in block 4 is better than in block 1

If we assume some level of transfer, than the average or individual performance in block 4 should be better in all conditions than in block 1 or potentially in block 2. I don't test for block 3 because that immediately compares the switch performance. 
```{r, echo=F,message=F}
make_graph(sub_walk_all[sub_walk_all$exp_block_id %in% c(1,4),], "learning.condition", "min_norm_distance", "exp_block_id") + 
  ylab("Average normalised trial distance") + xlab("condition") + 
  scale_fill_manual(values=estimote_pal,"Block ID")
make_graph(sub_walk_all[sub_walk_all$exp_block_id %in% c(1,4),], "learning.condition", "errors", "exp_block_id") + 
  ylab("Average number of errors") + xlab("condition") + 
  scale_fill_manual(values=estimote_pal,"Block ID")
```

@@

Within subject anova shows a significant effect of phase and condition on overall performance, but not of their interaction.
```{r, echo=F}
fit_dist_phase <- lmer(min_norm_distance ~ phase*learning.condition + (1 | id/phase), data = sub_walk_all)
kable(mixed_table_report(fit_dist_phase))
pair_t_norm_distance_phase_2 <- pairwise.t.test(sub_walk_all$min_norm_distance, sub_walk_all$learning.condition, p.adj = "holm")
```

Performance in the second phase differs significantly between groups (`r apa_print(aov(min_norm_distance ~ learning.condition, sub_walk_all[sub_walk_all$phase == 2,]))$statistic$learning_condition`), suggesting that the learnign modality has an effect on the overall performance. Tukey test shows significant difference between real adn a desktop versions. although this can be only because of bad performance in block 4 after switch, not due to blocks 5 and 6 (will test later.)

@@

Anova shows significant effect of both phase, learning condition and their interaction on pointing performance. Probably due to the fact that participants pointed less acurately on the treadmill and evn less on the desktop, but all then achieved same performance by the end of the 6th block.

```{r, echo=F}
fit_angle_phase <- lmer(abs_error ~ phase*learning.condition + (1 | id/phase), data = sub_sop_all)
kable(mixed_table_report(fit_dist_phase))
```

### Average walking performance in block 3 vs 4

@@

Within subject anova shows significant effect of both block and its interaction on distance walked.
```{r, echo=F}
fit_dist_34 <- lmer(min_norm_distance ~ exp_block_id*learning.condition + (1 | id/phase), data = sub_walk_all[sub_walk_all$exp_block_id %in% c(3,4),])
kable(mixed_table_report(fit_dist_34))
```

And significant effect all both conditoin, block and their interaction on the number of errors.
```{r, echo=F}
fit_dist_34 <- lmer(errors ~ exp_block_id*learning.condition + (1 | id/phase), data = sub_walk_all[sub_walk_all$exp_block_id %in% c(3,4),])
kable(mixed_table_report(fit_dist_34))
```

Running separate pairwise t-tests to see individual performance change from block 3 to 4 gives the following results.
```{r, echo=F}
df_dist <- block_t_test(sub_walk_all, 3, 4,"min_norm_distance")[,c(1,4)]
df_error <- block_t_test(sub_walk_all, 3, 4,"errors")[,c(1,4)]
df34 <- merge(df_dist, df_error, by = "learning.condition")
colnames(df34) <- c("learning condition", "p-value distance improvement", "p-value errors improvement")
kable(df34, caption="Paired T test comparing infividual performance improvement from block 3-4 in different conditions")
```

@@

ggplot(clean_walk_34, aes(x = as.numeric(exp_block_id), y = errors, color = factor(condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(width=0.1), width = 0.2, geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_identity(), size = 1, geom="line") + 
  ylab("Average number of errors") + xlab("Experimental block") + 
  scale_color_manual(values = estimote_pal, "Learning condition")
```

### Personal walking performance change in block 1 vs 4 
(calculated as an average of individuals (block1-block4)/(block3+block4))
```{r, echo=F}
df_wide_errors$block14 <- (df_wide_errors$block1-df_wide_errors$block4)/(df_wide_errors$block1+df_wide_errors$block4)
df_wide_distance$block14 <- (df_wide_distance$block1-df_wide_distance$block4)/(df_wide_distance$block1+df_wide_distance$block4)
clean_walk_14 <- ez_prepare_block(sub_walk_all, c(1,4))
```

@@

### Learning modality has an effect on the learning curve (slope)
I hope mike or professor Ferer will help with this

### Level of correlation of personal performance in block 1,2,3 and 4

@@

POtential followups

### Difference in performance between groups in blocks 5 and 6

@@

### Difference in performance between groups in block 4-6 with inclusion of VR-VR group and real-VR group
